Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-08-02 text/paper/paper1.tex
materials modification

We constructed a set of 15 items for \as- and \es-sentences, respectively,
analogous to the examples in \ref{ex:as} and \ref{ex:es}. Sentences were
introduced by a subject {\small \acro{DP}}, including the quantifiers 
{\it alle diese} ("all of these") or {\it genau einer der} ("exactly 
one of these"), as well as the head noun which denoted different icons, 
such as letters or bells. Subjects were followed by an auxiliary, and 
a {\small \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun denoting 
a geometrical object, e.g. {\it einigen seiner Dreiecke/Quadrate} ("some of its triangles/squares").
The last word was the main verb {\it verbunden} ("connected"). Each sentence was recorded 
in a stressed and an unstressed version of scalar {\it einige} (see section xx 
below). As described above, three control sentences were created 
for each experimental item, corresponding to the critical positions
in the course of uncovering the accompanying sequences (see below).
The positional controls were recorded with neutral prosody.  Items
were evenly distributed across 5 lists using a Latin square design.

@@

>>>>

We constructed a set of 15 items for \as- and \es-sentences, respectively,
analogous to the examples in \ref{ex:as} and \ref{ex:es}. Sentences were
introduced by a subject {\small \acro{DP}}, including the quantifiers 
{\it alle diese} ("all of these") or {\it genau einer der} ("exactly 
one of these"), as well as the head noun which denoted different icons, 
such as letters or bells. Subjects were followed by an auxiliary, and 
a {\small \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun denoting 
a geometrical object, e.g. {\it einigen seiner Dreiecke/Quadrate} ("some of its triangles/squares"). The possessive pronoun was used in order to fix relative 
quantifier scope to surface scope, thus ensuring that {\it einige} has 
embedded status. The last word was the main verb {\it verbunden} ("connected"). 
Each sentence was recorded  in a stressed and an unstressed version of scalar 
{\it einige} (see section xx  below). As described above, three control sentences were created 
for each experimental item, corresponding to the critical positions
in the course of uncovering the accompanying sequences (see below).
The positional controls were recorded with neutral prosody.  Items
were evenly distributed across 5 lists using a Latin square design.

@@

\paragraph{Pictures.}
The visual sequences accompanying each sentence consisted of pictures comparable to those illustrated in Figure \ref{fig:InitialPicture}. In each picture, four alternative sub-scenarios were presented, in which an icon was surrounded by six geometrical shapes. Depending on the sentence material, shapes and icons differed across sentence types and conditions. For example, in our target conditions, 4 identical icons were surrounded by geometrical shapes that were all of the same type, whereas various iconds and surrounding elements were used in each sequence of the preference-related control structures. As described in section xx, grey colour initially covered the links between icons and shapes. As the connections were to be uncovered step by step, different pictures were designed corresponding to different stages in the uncovering process. Note that the single conditions impose distinct requirements on sequences. For instance, inherent entailment relations between \as-sentences and \es-sentences lead to different critical positions at which participants can make their judgments. We will therefore describe the sequences for each condition separately.

For \as-sentences, as well as for the corresponding positional control sentences described in Section \ref{sec:design}, we designed a set of seven pictures for each trial. In each sequence, the critical position associated with the literal meaning was presented at the third step, the position associated with the global meaning was shown at the fifth step, and the local reading was presented at the final step (see Figure \ref{fig:exseqAS} for an illustration of the critical positions). Pictures that were interspersed between these positions served as spillover-pictures. These were used in order to control for potentially delayed judgments and they additionally served as distractor items.

Sequences in the \es conditions (and their respective positional controls) consisted of a set of five pictures with the following critical positions. The critical positions as illustrated in Figure \ref{fig:exseqES} are associated with the second picture (global reading), the third picture (literal reading), as well as with the final picture (local reading).

For the preference-related controls, we used two types of sequences. First, a sequence in which the crirical position for the (preferred) Late Closure reading was presented preceding the critical position for the Early Closure reading ({\it LC sequence}), and second, a sequence in which the readings were presented in reversed order ({\it EC sequence}. In the LC sequences, seven pictures were presented, with the LC reading given at the third picture, aand the EC reading at the sixth picture. EC sequences consisted of five pictures, in which the critical positions were realized at the third picture (EC reading) and at the fifth picture (LC reading).

Finally, we added pictures compatible with unrelated fillers with critical position at random uncovering stages.

\paragraph{Lists.}
Experimental items and preference-related fillers were evenly distributed across lists. For the \as- and \es-sentences together with their respective controls, five lists were used employing a Latin square design. Picture sentence-pairs for the preference-related controls were spread across eight lists. Each target list was combined with each list from the preference-related controls, thus yielding to a total of forty lists. The thirty unrelated filler items were included in each of these resulting lists.
